%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% bookman, charter, courier, euro, eurosym, marvosym, mathpazo, palatino, pxfonts, times, txfonts, utopia, wasysym, tgbonum, tgcursor, lmodern, tgheros, tgadventor, tgpagella
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Chun Lu} \\ \vspace{1pt}
    \href{mailto:chun.lu.dev@gmail.com}{\underline{chun.lu.dev@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/chun-lu/}{\underline{https://www.linkedin.com/in/chun-lu/}} $|$
    \href{https://chunlu.github.io/}{\underline{https://chunlu.github.io/}} $|$
    \small 917-838-8738 
\end{center}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, Java, Javascript, C\#} \\
     \textbf{Front-End}{: React, Bootstrap, CSS, HTML} \\
     \textbf{Back-End}{: FastAPI, Django, Django Rest Framework, Flask} \\
     \textbf{Databases}{: PostgreSQL, MongoDb, Redis} \\
     \textbf{DevOps}{: Ansible, Docker, Podman, GitLab CI, GitHub Actions} \\
     \textbf{Additional Tools}{: Git, AWS, REST, GraphQL, Poetry, YAML, Jinja, Node.js, SQL, Jira, OKTA}
     }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer}{March 2025 -- Current}
      {M\&C Saatchi World Services}{New York, NY}
      \resumeItemListStart
        \resumeItem{Designed and deployed a geospatial analysis backend application using FastAPI, PostgreSQL, Redis, and AWS, enabling scalable and reliable data processing.}
        \resumeItem{Optimized database performance by implementing indexes and composite indexes, reducing query times and improving system responsiveness.}
        \resumeItem{Automated PowerPoint report generation by collaborating with cross-functional teams to identify requirements, consolidating common elements, and building a scalable reporting workflow.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{July 2018 -- February 2025}
      {Naval Information Warfare Center Pacific (NIWC PAC)}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Developed a Java-based mobile asset tracking application for inventory management and location services, streamlining the inventory process and improving overall operational efficiency.}
        \resumeItem{Designed and optimized database schema to capture devices and connections of the network infrastructure.}
        \resumeItem{Orchestrated automated provisioning of network infrastructure across multiple sites, including device configuration, connection establishment, and IP address management.}
        \resumeItem{Implemented unit tests leading to a reduction in manual testing time and an improvement in codebase maintainability.}
        \resumeItem{Developed and implemented a GitLab CI pipeline for automated build, test, and deployment. This pipeline streamlines the development workflow by automating tasks like testing and image builds, leading to improved efficiency.}
        \resumeItem{Migrated queries from REST to a single, optimized GraphQL request, simplifying data retrieval and codebase. This enhanced maintainability, promoting faster development cycles and improved code quality.}
        \resumeItem{Contributed to the development of a full-stack web application using React, Django Rest Framework, and Postgres. This application facilitates efficient 3D file hosting and management.}
        \resumeItem{Pioneered the development of interactive 3D PDFs for component visualization using custom LaTeX templates and embedded U3D models. This innovative approach leverages LaTeX's capabilities to generate dynamic 3D content within PDFs, enhancing usability and accessibility for users.}
        \resumeItem{Improved the existing system by adding a real-time data processing and visualization system using C\# and XML to handle GPS satellite data. This feature eliminates the need for post-processing with external software resulting in faster analysis and testing.}
        \resumeItem{Developed a Python-based tool using the Pandas library to refine and validate raw sensor data logs. This tool automatically eliminates inconsistencies like outliers and missing values, and auto-generates relevant plots and graphs (e.g., histograms, time series) for analysis. This resulted in a significant reduction in data preparation time, enabling faster and more efficient data analysis.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


% %-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd

%-----------Certifications-----------
\section{Certifications and Clearances}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AWS Certified Cloud Practitioner}{}
      {Validation Number: 85534bca94154672addb7967254a3e78}{January 22, 2024 -- January 22, 2027}    
    \resumeSubheading
      {Secret Clearance}{}
      {Active}{July 2019 -- July 2028}
  \resumeSubHeadingListEnd

% %-----------Clearances-----------
% \section{Clearances}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Secret Clearance}{}
%       {Active}{July 2019 -- July 2028}
%   \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {Bachelor of Engineering, Computer Engineering}{August 2014 -- May 2018}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}